My title

### 2024-03-12 paper/paper.qmd

This report consists of four sections, not including the introduction. In Section 2, we look at the data used for our report and include some tables and graphs to illustrate the different groups of people in our data. In section 3, we build the model and discuss its justification and explanation. The results of our predictions is highlighted in the Section 4 using tables and graphs. Lastly, discussions are conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.

In this report, R statistical programming language is used, with R packages: [a lot of citations needed]

@@

# Modify the x-axis limits
model_plot + xlim(-5, 5) +  # Adjust the limits as needed
  labs(x = "90% Credibility Interval")

# Discussion

>>>>

The remainder of this paper is structured into different sections. @sec-data demonstrates the data used for our report and includes some tables and graphs to illustrate the different groups of people in our data. @sec-model builds the model and discusses its justification and explanation. @sec-result highlights the results of the predictions using tables and graphs. @sec-discussion contains discussions that conducted based on the findings, which addresses the voting prediction results based on race, region, and employment status.

@@

# Modify the x-axis limits
model_plot + xlim(-5, 5) +  # Adjust the limits as needed
  labs(x = "90% Credibility Interval")
```

# Discussion {#sec-discussion}
